---
title: "Supplementary Information - Survey methods and results"
author: "Malgorzata Lagisz"
date: "20/02/2024"
output:
  html_document: 
   toc: true
   toc_depth: 5
   number_sections: false
   theme: united
   highlight: tango
  word_document: 
   toc: true
   toc_depth: 5
   number_sections: false
   highlight: tango
format:
  html:
    embed-resources: true
editor_options:
  chunk_output_type: console
---

This document contains supplementary methods, results and code for: 

"A practical guide to evaluating sensitivity of literature search strings for systematic reviews using relative recall"  

by   

Malgorzata Lagisz, Yefeng Yang, Sarah Young, Shinichi Nakagawa.   


NOTE: project GitHub repository with all data and code can be found at https://github.com/mlagisz/method_benchmarking_survey (it will be archived to Zenodo when manuscript is accepted for publication).   


# Project set up   

Loading packages and general settings.   

```{r}
#set global code chunk parameters for knitting:  
knitr::opts_chunk$set(echo = TRUE)

#load libraries (install if absent):  
pacman::p_load(tidyverse, #various tools
               here, #easy file paths
                DT, #data tables
                knitr, #document knitting
                wacolors, #color-blind friendly color palettes
                patchwork
                # ggimage, #adding images
                # ggcharts, #plots functionality
                # scales, #plots extra
                # readxl, #loading Excel
                # forcats, #category wrangling
                # ggupset, #upset plots
                # patchwork, #plot assembly
                # stringr, #text wrangling
                # ggbeeswarm, #beeswarm plots
                # tidytext, #text processing
                # stopwords, #text processing
                # tokenizers, #text processing
                # ggpatterns, #patterning for plots
                # lme4, #linear models
                # sjPlot
               )

## may need:
# install.packages("remotes")
# remotes::install_github("coolbutuseless/ggpattern")
#library(ggpattern)

## set a global plotting theme with background transparency:   
theme_set(theme_classic(base_size = 14) + 
            theme(panel.background = element_blank(), 
                  plot.background = element_blank(), 
                  legend.background = element_blank(), 
                  text = element_text(colour = "white")))
```

# Literature survey methods

## Survey protocol    

Before conducting the survey (before data collection) we registered our project protocol.    
The protocol is available on OSF at https://osf.io/wq6dh.   

## Deviations from survey protocol   

We did not deviate from our survey protocol except aggregating search sources with frequency less than 10% into "other" category in the plots showing our results.   

## Survey aims    

To evaluate current practices in search string validation/evaluation/testing/benchmarking across disciplines.   

## Survey methods     

We conducted two separate literature surveys using two representative surveys of 100 samples from recent systematic reviews and protocols, respectively.     
Survey1 covered systematic reviews published across journals and disciplines and Survey 2 focused on systematic reviews protocols published in Cochrane Reviews. Due to differences among disciplines in the degree of adoption of published protocols we did not use protocols in Survey1. In contrast, Cochrane Reviews have an established standard for publishing protocols and they are all related to medical sciences. Also, the search strategy for Cochrane reviews is usually developed at the protocol stage and is expected to be described in detail in the protocol with the final report referring to the details in the published protocol.       


### Survey1 - workflow  

 1. Collecting a sample of general-population systematic reviews published in 2022 using Scopus database search string TITLE ( systematic*  W/3  review* )  AND  ( LIMIT-TO ( PUBYEAR ,  2022 ) ). Over 45,000 records were available for sampling.   
 2. Drawing a random sample of 100 records published in 2022.     
 3. Articles without full text available, articles in languages other than English, and articles that were not systematic reviews were excluded. We then iteratively substituted excluded articles with another randomly drawn article with full text available, until we had a sample of 100 eligible systematic reviews articles for assessment.   
 4. Performing data extraction and coding using pre-piloted GoogleForm, as described below.   
 5. Summarizing the extracted data.   

### Survey2 - workflow   

 1. Collecting a sample of systematic reviews protocols  from Cochrane Reviews protocols published in 2022 Issues 1-12. Approximately 220 document records were available for sampling.   
 2. Drawing a random sample of 100 Cochrane Reviews protocols published in 2022 (excluding sub-categories of Prototypes, Overviews, Methodology, Rapid Reviews, etc., which are not representative of a typical systematic review protocol) and checking for full text availability.   
 3. Articles without full text available were iteratively substituted with another randomly drawn article from the search, until we have a sample of 100 eligible articles with full text available for assessment.     
 4. Performing data extraction and coding using pre-piloted GoogleForm, as described below (same as for Survey1).        
 5. Summarizing the extracted data.    


### Data extraction    

For each article, ML manually extracted:    

 1. Information on article identity: DOI, title, first author name, publication journal (full reference will be also archived separately).   
 
 2. Information on search sources: literature sources (e.g.online databases/platforms) used for the systematic review following 28 most commonly used as listed in Gusenbauer, M, Haddaway, NR. (Which academic search systems are suitable for systematic reviews or meta-analyses? Evaluating retrieval qualities of Google Scholar, PubMed, and 26 other resources. Res Syn Meth. 2020; 11: 181–217;doi:10.1002/jrsm.1378) [checkboxes to code the most common 28 search platforms/databases and an option to add and describe other sources].   
 
 3. Information on search strategy reporting, development, and search string sensitivity assessment/validation:    
     - whether any description is provided of search string development(i.e. providing a description of how the final search string was arrived at by describing term harvesting techniques, iteration methods, testing strategies, etc. for at least one database; if none or only final search strings are reported select "no") [values: yes / no / unclear],     
     - notes and text quotations describing search string development approach (for at least one literature source) [values: free text],    
     - whether explicit recordof search string development is provided for at least one online database (e.g. as a table of consecutive search string variants used before setting on the final one) [vslues: yes / no / unclear],  
     - notes and text quotations describing search string development record [values: free text],   
     - whether a final search stringis provided for at least one source (e.g., in text or as a table -this is sometimes included in supplements for one or more databases). Note that there are two levels of "no" and two levels of "yes" [values: no (no search strategy reported or only searched sources) / no (full or partial list of keywords used given in text but no exact search) / yes (exact search strategy for at least one source) / yes (exact search strategy for all sources) / unclear],   
     - notes and text quotations describing where and how a final search string is reported for at least one source and/or write a comment (e.g., "Table S1 in SI") [values: free text],    
     - whether a predefined set of papers was used to seedsearch string development [values: yes / no / unclear],   
     - terms used to describe predefined set of papers used for search string development [values: free text / NA],   
     - whether full text or SI mentions any type of search string sensitivity evaluationfor at least one literature source [values: yes / no / unclear],     
     - notes and text quotations describing search string sensitivity evaluation approach [values:free text],   
     - number of literature sources (e.g., online databases/platforms) for which search string sensitivity evaluation was conducted [values: numeric -integer], 
     - names of literature sources (e.g.,online databases/platforms) for which search string sensitivity evaluation was conducted [values: free text],  
     - whether a predefined set of papers was used to evaluate the developed search string in terms of sensitivity [values: yes / no / unclear],  
     - terms used to describe the predefined set of papers used for search string sensitivity evaluation [values: free text / NA],  
     - terms used to describe the search string sensitivity evaluation (e.g., validation, evaluation, testing, benchmarking) [values: free text / NA],  
     - number of papers used in the predefined set of papers used for search string development (either seeding or evaluation) [values: numeric -integer],  
     - notes on the reported way of assembling the set of papers used for search string development (either seeding or evaluation) [values: free text / NA],  
     - notes and text quotations describing the search string sensitivity testing approach [values: free text].  
     
 4. Information on whether an information specialist was involved in the development of search strategies:   
 
     - whether any information specialist (e.g., a librarian) was involved in the systematic review [values: yes / no / unclear],  
     - notes and text quotations describing involvement of an information specialist [values: free text].   
 
### Data cross-checking    

Extracted data were  independently cross-checked by a second reviewer (YY - Survey1, SY - Survey2).    
Disagreements or unclear data were resolved to consensus via comments provided to the original reviewer and discussion, as needed.   

### Data analyses    

ML used the R computational environment for final data cleaning, summaries, analyses, and visualizations, with code versioning via git and GitHub. For Survey1 and Survey2, we summarized manually coded data using simple tables of counts. We then visualized the results as bar plots of proportions. All data processing and visualisation code is provided below.    


# Literature survey results  

## Load and check data   

```{r}
## Load extracted data (add an associated meta-data table later), preliminary clean and overview:   
mydat <- read.csv(here("data", "Benchmarking_lit_survey_(cross-checked) - Form Responses 1.csv")) 
#str(mydat)
#names(mydat)
names(mydat) <- gsub(" ", "_", names(mydat)) #change spaces to _ in the column names
names(mydat) <- gsub("\\.","", names(mydat)) #remove . the column names
names(mydat) <- gsub("Searchsources","Search_sources", names(mydat)) #remove . the column names

mydat <- mydat %>% select(!ends_with("1")) #remove old empty columns
#names(mydat)

#add a new column for Cochrane vs other journals
mydat$Survey <- ifelse(mydat$Article_journal == "Cochrane Database of Systematic Reviews", "Cochrane", "other")
#table(mydat$Survey)
mydat$Survey <- factor(mydat$Survey) # convert to factor
mydat$Survey <- ordered(mydat$Survey, levels = c("other", "Cochrane")) #reorder levels

#table(mydat$Checker_initials, mydat$Survey, useNA = "always")
#table(mydat$String_development_described, mydat$Survey, useNA = "always")
#table(mydat$String_development_record_provided, mydat$Survey, useNA = "always")
#table(mydat$String_development_seed_papers_used, mydat$Survey, useNA = "always")
#table(mydat$String_sensitivity_evaluation_mentioned, mydat$Survey, useNA = "always") #only one review tested for 1 source, in each Survey
#mydat[mydat$String_sensitivity_evaluation_mentioned == "yes", ] #see 2 reviews that did sensitivity evaluation

#table(mydat$String_sensitivity_evaluation_source_number, mydat$Survey, useNA = "always") #only one review tested for 1 source, in each Survey
#table(mydat$String_sensitivity_test_papers_used, mydat$Survey, useNA = "always") #only one review
#table(mydat$String_sensitivity_test_papers_terminology, mydat$Survey, useNA = "always") #benchmarking, validation
#table(mydat$String_sensitivity_test_papers_number, mydat$Survey, useNA = "always") #105 once, in other journal Survey
#table(mydat$String_sensitivity_test_papers_sources, mydat$Survey, useNA = "always") #known set
#table(mydat$String_sensitivity_test_approach, useNA = "always") #benchmarking
#table(mydat$Information_specialist_involved, mydat$Survey, useNA = "always")
#table(mydat$Final_string_provided, mydat$Survey, useNA = "always") #4 levels of response
#table(mydat$Search_sources, mydat$Survey, useNA = "always") #needs processing
#table(is.na(mydat$Search_sources)) #note no empty values 
```

## List of extracted papers for Survey1 and Survey2   

### Survey 1 - cross-disciplinary sample of 100 systematic reviews  

Create a table of extracted articles for Survery1.   

```{r}
mydat %>% filter(Survey == "other") %>% select(Article_DOI, Article_author, Article_journal, Article_title) %>% arrange(Article_author, Article_journal, Article_title) -> mydat_other_articles

#create a html table for mydat_other_articles   
mydat_other_articles %>%
  datatable(extensions = 'Buttons', 
            options = list(
              dom = 'Bfrtip',
              buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
              pageLength = 20
            ))

## making a html table for saving SI into the pdf:
# kable(mydat_other_articles, "html") #%>%
  ##kable_styling("striped", position = "left") #%>%
  ##scroll_box(width = "100%", height = "1500px")
```

### Survey 2 - sample of 100 Cochrane Reviews protocols  

```{r}
mydat %>% filter(Survey == "Cochrane") %>% select(Article_DOI, Article_author, Article_journal, Article_title) %>% arrange(Article_author, Article_journal, Article_title) -> mydat_Cochrane_articles

#create a html table for mydat_other_articles   
mydat_Cochrane_articles %>%
  datatable(extensions = 'Buttons', 
            options = list(
              dom = 'Bfrtip',
              buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
              pageLength = 20
            ))

## making a html table for saving SI into the pdf:
# kable(mydat_Cochrane_articles, "html") #%>%
  ##kable_styling("striped", position = "left") #%>%
  ##scroll_box(width = "100%", height = "1500px")
```

## Process and plot extracted data for each key extracted vairiable   

### String_development_described

```{r}
panel_String_development_described <- 
  mydat %>% 
  group_by(Survey) %>%
  count(String_development_described) %>%
  ggplot(aes(x = Survey, 
             y = n, 
             fill = String_development_described)) +
  geom_bar(aes(fill = String_development_described), 
           stat = "identity", 
           position = "fill") + # use , position = "fill" for proportion plot
  coord_flip() + 
  scale_fill_manual(values = c("#21281D", "#BAAF9F"),
                    guide = guide_legend(reverse = TRUE)) +
  theme_bw() +
  theme(legend.position = "top", 
        legend.box = "horizontal", 
        axis.text = element_text(size = 10)) +
  labs(fill = "Search string development described in detail?") +
  labs(x = "Survey", 
       y = "Article proportion")  

panel_String_development_described
```

### String_development_record_provided

```{r}
panel_String_development_record_provided <- 
  mydat %>% 
  group_by(Survey) %>%
  count(String_development_record_provided) %>%
  ggplot(aes(x = Survey, 
             y = n, 
             fill = String_development_record_provided)) +
  geom_bar(aes(fill = String_development_record_provided), 
           stat = "identity", 
           position = "fill") + # use , position = "fill" for proportion plot
  coord_flip() + 
  scale_fill_manual(values = c("#21281D", "#BAAF9F"),
                    guide = guide_legend(reverse = TRUE)) +
  theme_bw() +
  theme(legend.position = "top", 
        legend.box = "horizontal", 
        axis.text = element_text(size = 10)) +
  labs(fill = "Search string development record provided?") +
  labs(x = "Survey", 
       y = "Article proportion")  

panel_String_development_record_provided
```

### String_development_seed_papers_used

```{r}
panel_String_development_seed_papers_used <- 
  mydat %>% 
  group_by(Survey) %>%
  count(String_development_seed_papers_used) %>%
  ggplot(aes(x = Survey, 
             y = n, 
             fill = String_development_seed_papers_used)) +
  geom_bar(aes(fill = String_development_seed_papers_used), 
           stat = "identity", 
           position = "fill") + # use , position = "fill" for proportion plot
  coord_flip() + 
  scale_fill_manual(values = c("#21281D", "#BAAF9F"),
                    guide = guide_legend(reverse = TRUE)) +
  theme_bw() +
  theme(legend.position = "top", 
        legend.box = "horizontal", 
        axis.text = element_text(size = 10)) +
  labs(fill = "Seed papers used in string development?") +
  labs(x = "Survey", 
       y = "Article proportion")  

panel_String_development_seed_papers_used
```

### String_sensitivity_evaluation_mentioned

```{r}
panel_String_sensitivity_evaluation_mentioned <- 
  mydat %>% 
  group_by(Survey) %>%
  count(String_sensitivity_evaluation_mentioned) %>%
  ggplot(aes(x = Survey, 
             y = n, 
             fill = String_sensitivity_evaluation_mentioned)) +
  geom_bar(aes(fill = String_sensitivity_evaluation_mentioned), 
           stat = "identity", 
           position = "fill") + # use , position = "fill" for proportion plot
  coord_flip() + 
  scale_fill_manual(values = c("#21281D", "#BAAF9F"),
                    guide = guide_legend(reverse = TRUE)) +
  theme_bw() +
  theme(legend.position = "top", 
        legend.box = "horizontal", 
        axis.text = element_text(size = 10)) +
  labs(fill = "String sensitivity evaluation mentioned?") +
  labs(x = "Survey", 
       y = "Article proportion")  

panel_String_sensitivity_evaluation_mentioned
```

### Information_specialist_involved

```{r}
panel_Information_specialist_involved <- 
  mydat %>% 
  group_by(Survey) %>%
  count(Information_specialist_involved) %>%
  ggplot(aes(x = Survey, 
             y = n, 
             fill = Information_specialist_involved)) +
  geom_bar(aes(fill = Information_specialist_involved), 
           stat = "identity", 
           position = "fill") + # use , position = "fill" for proportion plot
  coord_flip() + 
  scale_fill_manual(values = c("#21281D", "#BAAF9F"),
                    guide = guide_legend(reverse = TRUE)) +
  theme_bw() +
  theme(legend.position = "top", 
        legend.box = "horizontal", 
        axis.text = element_text(size = 10)) +
  labs(fill = "Information specialist mentioned?") +
  labs(x = "Survey", 
       y = "Article proportion")  

panel_Information_specialist_involved
```

### Final_string_provided

```{r}
#wacolors$diablo #preview colour-blind scale used

panel_Final_string_provided <- 
  mydat %>% 
  group_by(Survey) %>%
  count(Final_string_provided) %>%
  ggplot(aes(x = Survey, 
             y = n, 
             fill = Final_string_provided)) +
  geom_bar(aes(fill = Final_string_provided), 
           stat = "identity", 
           position = "fill") + # use , position = "fill" for proportion plot
  coord_flip() + 
  guides(fill = guide_legend(ncol = 2)) +
  scale_fill_manual(values = c("#172512", "#005929", "#279085", "#87C8D8"), #four custom colors
                    guide = guide_legend(reverse = TRUE)) +
  theme_bw() +
  theme(legend.position = "top", 
#        legend.direction = "vertical",
#        legend.box = "horizontal", 
        axis.text = element_text(size = 10)) +
  labs(fill = "Final search strings provided?") +
  labs(x = "Survey", 
       y = "Article proportion")  

panel_Final_string_provided
```

### Search_sources

```{r}
#table(mydat$Search_sources, mydat$Survey, useNA = "always") #needs processing

# process Search_sources
mydat$Scopus <- str_count(mydat$Search_sources, pattern = "Scopus")
mydat$WoS <- str_count(mydat$Search_sources, pattern = "Web of Science")
mydat$WoS <- ifelse(mydat$WoS == 0, 0, 1) #collapse to 2 levels: 0, 1
mydat$WHO_ICTRP <- str_count(mydat$Search_sources, pattern = "WHO")
mydat$WHO_ICTRP <- ifelse(mydat$WHO_ICTRP == 0, 0, 1) #collapse to 2 levels: 0, 1
mydat$PubMed <- str_count(mydat$Search_sources, pattern = "PubMed")
mydat$EbscoHost <- str_count(mydat$Search_sources, pattern = "EbscoHost")
mydat$OVID_Embase <- str_count(mydat$Search_sources, pattern = "OVID")
mydat$OVID_Embase <- ifelse(mydat$OVID == 0, 0, 1) #collapse to 2 levels: 0, 1
#mydat$ScienceDirect <- str_count(mydat$Search_sources, pattern = "ScienceDirect") #code as "other" below
#mydat$ProQuest <- str_count(mydat$Search_sources, pattern = "ProQuest")  #code as "other" below
mydat$other <- str_count(str_to_lower(mydat$Search_sources), pattern = c("sciencedirect|proquest|other|researchers|authors|references|related|registry|handsearching|internet|websites|google|scholar|personal|similar|open|zenodo|cnki|pistemonikos|unspecified|chinese|iran|islamic|nhs|briggs|xiv|abstracts|conference|ultimate|grey|wanfang|square|dimensions"))
#table(mydat$other, mydat$Survey)

#approx. how many sources used per article?
mydat$sum_sources <- mydat$Scopus + mydat$WoS + mydat$WHO_ICTRP + mydat$PubMed + mydat$EbscoHost + mydat$OVID_Embase + mydat$other 
min(mydat$sum_sources)
max(mydat$sum_sources)
median(mydat$sum_sources)
#hist(mydat$sum_sources)

mydat %>%
  ggplot( aes(x = sum_sources, fill = Survey)) +
    geom_histogram(color = "#e9ecef", alpha = 1, position = 'identity', binwidth = 1) +
    scale_fill_manual(values=c("#e9ecef", "#e9ecef")) +
    labs(x = "Number of sources searched", y = "Article proportion", fill = "") + 
    theme_bw() +
    theme(
      legend.position="none",
      panel.spacing = unit(0.1, "lines"),
      strip.text.x = element_text(size = 8)
    )  +
    facet_wrap(~ factor(Survey, levels = c("Cochrane", "other"), 
                  labels = c("Cochrane journal", "Other journals")), ncol = 2)

#prep for the barplot of counts per main  source type
mydat$other <- ifelse(mydat$other == 0, 0, 1) #collapse to 2 levels: 0, 1 #aggregate all "other" per article into a single count (1)

# Reshape to a long data format
longer_data <- mydat %>% 
  select(Survey, Scopus:other) %>% 
  pivot_longer(Scopus:other, names_to = "Source", values_to = "use") %>%
  arrange(Source, Survey) %>%
  mutate(Use = ifelse(use == 1, "yes", "no"))
print(longer_data)
str(longer_data)

longer_data$Source <- factor(longer_data$Source, levels = c("other","Scopus","PubMed","WoS","EbscoHost","WHO_ICTRP","OVID_Embase"), ordered = TRUE)

# plot counts from Search_sources
panel_search_sources <- 
  longer_data %>% 
  group_by(Survey, Source) %>%
  count(Use) %>%
  ggplot(aes(x = Source, 
             y = n, 
             fill = Use)) +
  geom_bar(aes(fill = Use), 
           stat = "identity", 
           position = "fill") + # use , position = "fill" for proportion plot 
  facet_wrap(~ factor(Survey, levels = c("Cochrane", "other"), 
                  labels = c("Cochrane journal", "Other journals")), ncol = 2) +
  coord_flip() + 
  scale_fill_manual(values = c("white", "#759C44"), #four custom colors
                    guide = guide_legend(reverse = TRUE)) +
  theme_bw() +
  theme(legend.position = "none", 
        legend.direction = "horizontal",
        legend.box = "horizontal", 
        axis.text = element_text(size = 10)) +
  labs(fill = "used") +
  labs(x = "Sources searched", 
       y = "Article proportion")  

panel_search_sources
```


## Combined figure   

Main manuscript figure - ombine all relevant panels to and save.    

```{r}
#assemble the panels using patchwork package
figure1 <- (panel_String_development_described /
              panel_String_development_record_provided /
              panel_String_development_seed_papers_used /
              panel_String_sensitivity_evaluation_mentioned /
              panel_Information_specialist_involved /
              panel_Final_string_provided /
              panel_search_sources) +
              plot_annotation(tag_levels = "A") +
  plot_layout(widths = c(1, 1, 1, 1, 1, 1, 1), 
              heights = c(1, 1, 1, 1, 1, 1, 3)) 

#ggsave(plot = figure1, here("plots", "Fig_survey_results_v0.png"), width = 16, height = 19, units = "cm", dpi = "retina", scale = 1.8)
#ggsave(plot = figure1, here("plots", "Fig_survey_results_v0.pdf"), width = 16, height = 19, units = "cm", scale = 1.8)
```

## Statitical tests    

Perform Fisher's Exact Tests for Information_specialist_involved and Final_string_provided variables.    

```{r}
#Information_specialist_involved vs Survey
M <- table(mydat$Survey, mydat$Information_specialist_involved)
fisher.test(M)


#table(mydat$Final_string_provided, mydat$Survey, useNA = "always") #4 levels of response
#M <- table(mydat$Survey, mydat$Final_string_provided)
#fisher.test(M) #hard to interpret

## Test exact search strategy for at least one source
#Final_string_provided = yes (exact search strategy for at least one source) vs. Survey
M <- table(mydat$Survey, mydat$Final_string_provided == "yes (exact search strategy for at least one source)")
fisher.test(M)

#Final_string_provided = yes (exact search strategy for at least one source) vs. Information_specialist_involved (both surveys)
M <- table(mydat$Final_string_provided == "yes (exact search strategy for at least one source)", mydat$Information_specialist_involved)
fisher.test(M)

## Test exact search strategy for all sources
#Final_string_provided = yes (exact search strategy for all sources) vs. Survey
M <- table(mydat$Survey, mydat$Final_string_provided == "yes (exact search strategy for all sources)")
fisher.test(M)

#Final_string_provided = yes (exact search strategy for all sources) vs. Information_specialist_involved (both surveys)
M <- table(mydat$Final_string_provided == "yes (exact search strategy for all sources)", mydat$Information_specialist_involved)
fisher.test(M)


## Cochrane survey
mydat_Cochrane <- mydat %>% filter(Survey == "Cochrane") #subset to Cochrane survey
M <- table(mydat_Cochrane$Final_string_provided, mydat_Cochrane$Information_specialist_involved)
fisher.test(M)
#Final_string_provided = yes (any)  vs. Information_specialist_involved (Cochrane survey)
M <- table(mydat_Cochrane$Final_string_provided == "yes (exact search strategy for at least one source)" | mydat_Cochrane$Final_string_provided == "yes (exact search strategy for all sources)", mydat_Cochrane$Information_specialist_involved)
fisher.test(M)



## Other survey
mydat_Other <- mydat %>% filter(Survey == "other") #subset to Other survey
M <- table(mydat_Other$Final_string_provided, mydat_Other$Information_specialist_involved)
fisher.test(M)

#Final_string_provided = yes (any)  vs. Information_specialist_involved (Other survey)
M <- table(mydat_Other$Final_string_provided == "yes (exact search strategy for at least one source)" | mydat_Other$Final_string_provided == "yes (exact search strategy for all sources)", mydat_Other$Information_specialist_involved)
fisher.test(M)

library("gplots")
# convert the data as a table
dt <- as.table(as.matrix(M))
# Graph
balloonplot(t(dt), main ="other journals survey", xlab ="Information_specialist_involved", ylab="Final_string_provided",
            text.size = 0.8, label = FALSE, show.margins = TRUE, cum.margins = FALSE)
```



## Session Info

Display all R session information.    

```{r}
sessionInfo()
```